---
title: "Small Sample July"
output: html_notebook
---

## Install libraries
```{r, echo=FALSE}
# install the library packages
library(rgdal)
library(sp)
library(sf)
library(raster)
library(leaflet)
library(leafpop)
library(mapview)
library(tidyverse)
library(censusxy)
library(tidycensus)
library(ggplot2)
library(RColorBrewer)
library(data.table)
library(fasttime)
library(sparklyr)
library(lubridate)
library(maps)
library(stringr)
```


```{r}
############################## Temporary
#setwd("C:/users/jd1/Desktop/ALL R Stuff and Research/Test_data_table")
#####################################################
# 1.  Collect St Louis City crime UCR statistics
# pull in state coordinate system files from st louis police reports using data.table
crime <- fread("C:/users/jd1/Desktop/ALL R Stuff and Research/Test_data_table/Group2018.csv", stringsAsFactors=FALSE)
```
## 2. look annd adjust the structure of the data

```{r}
crimeA <- crime %>% select(Complaint, CodedMonth, 
                                     DateOccur, Crime, Description, Neighborhood) %>%
            filter(Crime == 38111) 

```

## User stringr to add a day to the structure in preparation for creating a date field
```{r}
crimeA$CodedMonth <- str_c(crimeA$CodedMonth, "28", sep = "-")
summary(crimeA)

```
##  Look at the result of the string operation
```{r}

glimpse(crimeA)
```
## create a posix object for occurrance date
```{r}
crimeA$DateOccur <- mdy_hm(crimeA$DateOccur)
str(crimeA)
```
## create another date object  (****this one needs work - generating NAs***)
```{r}
crimeA$CodedMonth <- as_date(crimeA$CodedMonth)
str(crimeA)
```

## Check the finalized data structure
```{r}
summary(crimeA)
```

##  Make the date format structures compatable and calculate the difference in days the reporting delays.
```{r}
crimeB <- crimeA %>% mutate(Reporting.diff = CodedMonth - as_date(DateOccur))

```
##  Check on details
```{r}
glimpse(crimeB)
```

```{r}
## Now join neighborhoods with names
#add neighborhood shapes to a data frame
# From https://www.census.gov/geo/maps-data/data/cbf/cbf_state.html
hoods.sf <- readOGR("St Louis Shape files/nbrhds_wards/BND_Nhd88_cw.shp")
hoods.sf <- spTransform(hoods.sf, CRS("+proj=longlat +datum=WGS84"))
hoods <- mapview(hoods.sf, map.types = c("OpenStreetMap"),
                 layer.name = c("Neighborhoods"),
                 alpha.regions = 0.1,
                 alpha = 2,
                 zcol = c("NHD_NAME"))             
# collect neighborhood details from shape file
hoods.df <- as(hoods.sf, "data.frame")

```


```{r}
hoods.df %>% class()
glimpse(hoods.df)
```

## Trim neighborheads for joins
```{r}
crimeC <- hoods.df  %>% select(NHD_NUM, NHD_NAME)
crimeC$NHD_NUM <- as.integer(crimeC$NHD_NUM)
str(crimeC)
```
##  This is the join for neighborhoods


```{r}
# join carkacks table with hoods table to get neighborhood names

crimeD <- left_join(crimeB, crimeC, by = c("Neighborhood" = "NHD_NUM")) 

glimpse(crimeD)
```


```{r}
## Group by month and count for carjack
crimeA %>% 
  group_by(CodedMonth) %>%
  count(CodedMonth) %>%
  view()
###################################
```


```{r}



## Plot the count by month
crimeA  %>% 
  group_by(CodedMonth) %>%
  count(CodedMonth) %>% 
  ggplot(aes(x = CodedMonth, y = n)) +
  geom_col(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90)) # change tex to verticle
#################### (need to change legends)
str(crimeA)
```

```{r}

###########################################
## Group by Neighborhood and count
crimeD  %>% 
  group_by(NHD_NAME) %>%
  count(Neighborhood) %>%
 view()
#################################################

```

```{r}
## Plot the count by month
crimeD  %>% 
  group_by(NHD_NAME) %>%
  count(Neighborhood) %>% 
  ggplot(aes(x = NHD_NAME, y = n)) +
  geom_col(color = "cornflowerblue") +
  theme(axis.text.x = element_text(angle = 90)) # change tex to verticle
#################### (need to change legends)
str(crimeD)
```










